---
title: "HW 7: Shiny 1"
author: "Yashvi Malviya"
date: "`r Sys.Date()`"
output: html_document
urlcolor: "blue"
params:
  solutions: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

# Instructions

- Write your solutions in this starter file. You should modify the 
  "author" field in the YAML header.
- Place all of your Shiny code in this file. But make sure you have 
  `eval = FALSE` in your code-chunk options so that you don't 
  end up running the Shiny apps in the HTML file you generate.
- Only commit R Markdown and HTML files (no PDF files). Make sure
  you have knitted to HTML for your final submission.
- **Make sure to commit each time you answer a question.**
- Only include the necessary code, not any extraneous code, to answer the 
  questions.
- Learning objectives:
    - Practice developing simple Shiny Apps.
    
1. (3 pts) Create a Shiny app that takes as input three variables from the 
   `mpg` dataset from the `ggplot2` package. It will make a
   scatterplot of two of the variables and color code by the third variable.
   Make the default variables the ones in the image below. Your app 
   should look like this:
```{r eval=FALSE}
library(shiny)
library(ggplot2)

ui <- fluidPage(
    selectInput("var1", "X-Axis Variable", choices = names(mpg)),
    selectInput("var2", "Y-Axis Variable", choices = names(mpg)),
    selectInput("color_var", "Color Variable", choices = names(mpg)),
    plotOutput("plot")
)

server <- function(input, output) {
    output$plot <- renderPlot({
        ggplot(mpg, aes(x = .data[[input$var1]], y = .data[[input$var2]], color = .data[[input$color_var]])) +
            geom_point()
    })
}

shinyApp(ui = ui, server = server)

```

    
2. (3 pts) Create a [Mad Libs](https://en.wikipedia.org/wiki/Mad_Libs) Shiny App that
   takes as input 4 or 5 words and returns a paragraph where those words are
   populated inside specific locations of that paragraph. The inputs should
   be a [part of speech](https://en.wikipedia.org/wiki/Part_of_speech)
   (such as noun, verb, adjective, adverb, pronoun, preposition, 
   conjunction, or interjection). 
   
    Here is my example (but be creative with yours!):

```{r eval=FALSE}
library(shiny)

ui <- fluidPage(
  titlePanel("Mad Libs Shiny App"),
  sidebarLayout(
    sidebarPanel(
      textInput("noun", "Noun:", ""),
      textInput("verb", "Verb:", ""),
      textInput("adjective", "Adjective:", ""),
      textInput("adverb", "Adverb:", ""),
      textInput("pronoun", "Pronoun:", ""),
      actionButton("generate", "Generate Mad Lib"),
    ),
    mainPanel(
      textOutput("madlib_paragraph")
    )
  )
)


server <- function(input, output) {
  

  generate_madlib <- function() {
    madlib_paragraph <- paste(
      "The", input$noun, input$verb, "very", input$adjective,
      "and", input$adverb, ". Suddenly,", input$pronoun, "decided to go",
      "to the park, where they met a group of", input$noun, "who exclaimed, 'Wow!'"
    )
    return(madlib_paragraph)
  }
  
  observeEvent(input$generate, {
    madlib_text <- generate_madlib()
    output$madlib_paragraph <- renderText(madlib_text)
  })
}

shinyApp(ui = ui, server = server)


# Noun:
# Suggestions: "cat," "tree," "car," "book," "beach"
# 
# Verb:
# Suggestions: "ran," "sang," "built," "danced," "swam"
# 
# Adjective:
# Suggestions: "colorful," "mysterious," "tall," "delicious," "exciting"
# 
# Adverb:
# Suggestions: "quickly," "silently," "joyfully," "carefully," "unexpectedly"
# 
# Pronoun:
# Suggestions: "she," "he," "they," "it," "we"
```

3. (3 pts) Create a Shiny app that takes as input the variable from the `mtcars`
   dataset to plot as well as the type of plot (histogram, density, or 
   frequency polygon). Taking advantage of the 
   modular nature of ggplot2 will make your life easier:
   
    ``` r
    data("iris")
    pl <- ggplot(iris, aes(x = Species))
    pl
    
    pl <- pl + geom_bar()
    pl
    ```
   
    Your app should look like this:
```{r eval=FALSE}
library(shiny)
library(ggplot2)
library(dplyr)


ui <- fluidPage(
  titlePanel("ggplot2 Plot Selector"),
  sidebarLayout(
    sidebarPanel(
      selectInput("variable", "Select a Variable:", choices = names(mtcars)),
      radioButtons("plot_type", "Select Plot Type:", 
                   choices = c("Histogram", "Density", "Frequency")),
    ),
    mainPanel(
      plotOutput("plot")
    )
  )
)


server <- function(input, output) {
  
  output$plot <- renderPlot({
    variable_name <- input$variable
    plot_type <- input$plot_type
    
    data <- mtcars %>% 
      select(all_of(variable_name))
    
    gg <- ggplot(data, aes(x = .data[[variable_name]]))
    
    if (plot_type == "Histogram") {
      gg <- gg + geom_histogram()
    } else if (plot_type == "Density") {
      gg <- gg + geom_density()
    } else if (plot_type == "Frequency") {
      gg <- gg + geom_freqpoly()
    }
    
    print(gg)
  })
}

shinyApp(ui = ui, server = server)

```
